第 5 课
========================================================
```{r}
library(ggplot2)
library(dplyr)
library(gridExtra)

pf = read.delim('pseudo_facebook.tsv')
```

### 多变量数据
注释：

***

### 年龄标记为彩色的自我感知关注量
注释：

***

### 第三个定性变量
注释：

```{r Third Qualitative Variable}
ggplot(aes(x = gender, y = age),
       data = subset(pf, !is.na(gender))) + 
  geom_boxplot() +
  stat_summary(fun.y = mean, geom = 'point', shape = 4)

ggplot(aes(x = age, y = friend_count),
       data = subset(pf, !is.na(gender))) +
  geom_line(aes(color = gender), stat = 'summary', fun.y = median)
```
# Write code to create a new data frame,
# called 'pf.fc_by_age_gender', that contains
# information on each age AND gender group.

# The data frame should contain the following variables:

#    mean_friend_count,
#    median_friend_count,
#    n (the number of users in each age and gender grouping)
```{r}
age_gen_groups = group_by(subset(pf, !is.na(gender)), age, gender)
pf.fc_by_age_gender = summarise(age_gen_groups,
          mean_friend_count = mean(friend_count),
          median_friend_count = median(friend_count),
          n = n())
pf.fc_by_age_gender = ungroup(pf.fc_by_age_gender)
pf.fc_by_age_gender = arrange(pf.fc_by_age_gender, age)
```

***

### 绘制条件总结
注释：
# Create a line graph showing the
# median friend count over the ages
# for each gender. Be sure to use
# the data frame you just created,
# pf.fc_by_age_gender.
```{r Plotting Conditional Summaries}
ggplot(aes(x = age, y = median_friend_count), data = pf.fc_by_age_gender) +
  geom_line(aes(color = gender))
```

***

### 思考比率
注释：

***

### 又宽又长的格式
注释：

***

### 改变数据
注释：
# ~左边的是保留的变量
```{r}
install.packages('reshape2')
library(reshape2)

pf.fc_by_age_gender.wide = dcast(pf.fc_by_age_gender, 
      age ~ gender,
      value.var = 'median_friend_count')
```

***

### 比率图
注释：
# Plot the ratio of the female to male median
# friend counts using the data frame
# pf.fc_by_age_gender.wide.

# Think about what geom you should use.
# Add a horizontal line to the plot with
# a y intercept of 1, which will be the
# base line. Look up the documentation
# for geom_hline to do that. Use the parameter
# linetype in geom_hline to make the
# line dashed.

# The linetype parameter can take the values 0-6:
# 0 = blank, 1 = solid, 2 = dashed
# 3 = dotted, 4 = dotdash, 5 = longdash
# 6 = twodash
```{r Ratio Plot}
ggplot(aes(x = age, y = female / male), data = pf.fc_by_age_gender.wide) +
  geom_line() + 
  geom_hline(yintercept = 1, alpha = 0.3, linetype = 2)

```

***

### 第三个定性变量
注释：
# Create a variable called year_joined
# in the pf data frame using the variable
# tenure and 2014 as the reference year.

# The variable year joined should contain the year
# that a user joined facebook.

```{r Third Quantitative Variable}
pf$year_joined = 2014 - ceiling(pf$tenure / 365)
```

***

### 减少一个变量
注释：
# Create a new variable in the data frame
# called year_joined.bucket by using
# the cut function on the variable year_joined.

# You need to create the following buckets for the
# new variable, year_joined.bucket

#        (2004, 2009]
#        (2009, 2011]
#        (2011, 2012]
#        (2012, 2014]

```{r Cut a Variable}
summary(pf$year_joined)
table(pf$year_joined)

pf$year_joined.bucket = cut(pf$year_joined, breaks = c(2004, 2009, 2011, 2012, 2014))
```

***

### 同时绘制
注释：
# Create a line graph of friend_count vs. age
# so that each year_joined.bucket is a line
# tracking the median user friend_count across
# age. This means you should have four different
# lines on your plot.

# You should subset the data to exclude the users
# whose year_joined.bucket is NA.

```{r Plotting it All Together}
ggplot(aes(x = age, y = friend_count), 
       data = subset(pf, !is.na(year_joined.bucket))) +
  geom_line(aes(color = year_joined.bucket), 
            stat = 'summary',
            fun.y = median)

```

***

### 绘制总平均值
注释：
# Write code to do the following:

# (1) Add another geom_line to code below
# to plot the grand mean of the friend count vs age.

# (2) Exclude any users whose year_joined.bucket is NA.

# (3) Use a different line type for the grand mean.

# As a reminder, the parameter linetype can take the values 0-6:

# 0 = blank, 1 = solid, 2 = dashed
# 3 = dotted, 4 = dotdash, 5 = longdash
# 6 = twodash

```{r Plot the Grand Mean}
ggplot(aes(x = age, y = friend_count), 
       data = subset(pf, !is.na(year_joined.bucket))) +
  geom_line(aes(color = year_joined.bucket), 
            stat = 'summary',
            fun.y = mean) +
  geom_line(stat = 'summary', fun.y = mean, linetype = 2)
```

***

### 交友率
注释：

```{r Friending Rate}
with(subset(pf, tenure>=1), summary(friend_count / tenure))
```

***

### 开始交友
注释：

平均交友率是什么？

最大交友率是什么？

# Create a line graph of mean of friendships_initiated per day (of tenure)
# vs. tenure colored by year_joined.bucket.

# You need to make use of the variables tenure,
# friendships_initiated, and year_joined.bucket.

```{r Friendships Initiated}
ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket), 
            stat = 'summary',
            fun.y = mean)
```

***

### 再次访问方差权衡
注释：

# Instead of geom_line(), use geom_smooth() to add a smoother to the plot.
# You can use the defaults for geom_smooth() but do color the line
# by year_joined.bucket

```{r Bias-Variance Tradeoff Revisited}

p1 = ggplot(aes(x = tenure, y = friendships_initiated / tenure),
       data = subset(pf, tenure >= 1)) +
  geom_line(aes(color = year_joined.bucket),
            stat = 'summary',
            fun.y = mean)

p2 = ggplot(aes(x = 7 * round(tenure / 7), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

p3 = ggplot(aes(x = 30 * round(tenure / 30), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

p4 = ggplot(aes(x = 90 * round(tenure / 90), y = friendships_initiated / tenure),
       data = subset(pf, tenure > 0)) +
  geom_line(aes(color = year_joined.bucket),
            stat = "summary",
            fun.y = mean)

p5 = ggplot(aes(x = tenure, y = friendships_initiated / tenure),
            data = subset(pf, tenure > 0)) +
  geom_smooth(aes(color = year_joined.bucket))

grid.arrange(p1, p2, p3, p4, p5, ncol = 1)

```

***

### Sean 对 NFL 粉丝情绪的研究
注释：

***

###  Yogurt 数据集简介
注释：

***

### 再次访问直方图
注释：

```{r Histograms Revisited}
yo = read.csv('yogurt.csv')
str(yo)

yo$id = factor(yo$id)
str(yo)

ggplot(aes(x = price), data = yo) +
  geom_histogram()
```

***

### 购买数量
注释：
# Create a new variable called all.purchases,
# which gives the total counts of yogurt for
# each observation or household.

# One way to do this is using the transform
# function. You can look up the function transform
# and run the examples of code at the bottom of the
# documentation to figure out what it does.

# The transform function produces a data frame
# so if you use it then save the result to 'yo'!

```{r Number of Purchases}
yo = transform(yo, all.purchases = strawberry + blueberry + pina.colada +
                 plain + mixed.berry)
# yo$all.purchases = yo$strawberry + yo$blueberry + yo$pina.colada + yo$plain + yo$mixed.berry
```

***

### 一段时期的价格
注释：

# Create a scatterplot of price vs time.

# This will be an example of a time series plot.

# Resolve overplotting issues by using
# techniques you learned in Lesson 4.

# What are some things that you notice?

```{r Prices over Time}
ggplot(aes(x = time, y = price), data = yo) +
  geom_jitter(alpha = 1/4, shape = 21)
```

***

### 抽样观察
注释：

***

### 观察家庭的样本

```{r Looking at Sample of Households}
set.seed(4230)
sample.ids = sample(levels(yo$id), 16)

ggplot(aes(x = time, y = price),
       data = subset(yo, id %in% sample.ids)) +
  facet_wrap(~id) +
  geom_line() +
  geom_point(aes(size = all.purchases), pch = 1)
```

***

### 交叉分组数据的缺点
注释：

***

### 许多变量
注释：

***

### 散点图矩阵
注释：

***

### 更多变量
注释：

***

### 热点图
注释：

```{r}
nci <- read.table("nci.tsv")
colnames(nci) <- c(1:64)
```

```{r}
nci.long.samp <- melt(as.matrix(nci[1:200,]))
names(nci.long.samp) <- c("gene", "case", "value")
head(nci.long.samp)

ggplot(aes(y = gene, x = case, fill = value),
  data = nci.long.samp) +
  geom_tile() +
  scale_fill_gradientn(colours = colorRampPalette(c("blue", "red"))(100))
```

***

### 分析三个及三个以上变量
思考：

***

点击 **KnitHTML** 查看你的成果和这节课的 html 页面、
答案和注释！
